\mythesistitleNOTSYNPOSIS

### 2012-01-04 src/020chap2.tex
Added figure illustrating graph matrix definitions. Also - this is going SO slow. Fastfowrding on.

\begin{definition}{\emph{Matrices that define
      graphs.\cite[Def.~2.4]{d08phd}}} %
  \label{def:graphmatrices} %
  Let $G$ and $H$ be defined as follows. $G = (V,E_G)$ is a graph with
  vertex set $V = \{v_i \mid i \in [n]\}$ and edge set $E_G \subseteq
  \{(v_i,v_j) \mid i, j \in [n]\}$ such that $|E_G| = m$. $H = (A, B,
  E_H)$ is a bipartite graph with partitions $A = \{a_i \mid i \in
  [n_a]\}$ and $B = \{b_i \mid i \in [n_b]\}$.
  \begin{enumerate}[{\ref{def:graphmatrices}}--i.]
  \item \emph{Adjacency matrix} of $G$ is the symmetric $n \times n$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(v_i,v_j) \in E_G$
    for all $i,j \in [n]$.
  \item \emph{Augmented adjacency matrix} of $G$ is obtained from its
    adjacency matrix by setting all main diagonal elements to \un, \ie
    $m_{i,i} = \un$ for all $i \in [n]$.
  \item \emph{Maximal clique matrix} or \emph{vertex-clique incidence
      matrix} of $G$ is the $n \times k$ binary matrix $M$ with
    $m_{i,j} = \un$ \iff $v_i \in C_j$ for all $i \in [n], j \in [k]$
    where $\{C_j \mid j \in [k]\}$ is the set of maximal cliques of
    $G$.
  \item \emph{Half adjacency matrix} of $H$ is the $n_a \times n_b$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(a_i, b_j) \in E_H$
  \end{enumerate}
\end{definition}

@@

@@

   \begin{enumerate}[\ref{def:graphwithcop}--i.]
   \item $G$ is \emph{convex-round} if its adjacency matrix has the
     \CROP.
   \item $G$ is \emph{concave-round} if its augmented adjacency matrix
     has \CROP. \tnote{cite BHY00} \tnote[minor]{add CROP to glossary}
   \item $G$ is an \emph{interval graph} if its vertices can be mapped
     to intervals on the real line \stt two vertices are adjacent \iff
     their corresponding intervals overlap \tnote{cite Ben59, Haj57}.
     $G$ is an interval graph \iff its maximal clique matrix has COP
     due to the result by \cite{gh64} which states that the maximal
     cliques of interval graph $G$ can be linearly ordered \stt for
     all $v \in V(G)$, cliques containing $v$ are consecutive in the
     ordering.
   \item $G$ is a \emph{unit interval graph} if it is an interval
     graph \stt all intervals have the same length.
   \item $G$ is a \emph{proper interval graph} if it is an interval
     graph \stt no interval properly contains another.
   \item $G$ is a \emph{circular-arc graph} if its vertices can be
     mapped to a set of arcs on a circle \stt two vertices are
     adjacent \iff their corresponding arcs overlap.
   \item $H$ is \emph{convex bipartite} if its half adjacency matrix
     has \COP on either rows or columns.
   \item $H$ is \emph{biconvex bipartite} or \emph{doubly
       convex}\cite{yc95} if its half adjacency matrix has \COP on
     both rows and columns.
   \item $H$ is \emph{circular convex} if its half adjacency matrix
     has \CROP.
   \end{enumerate}
\end{definition}
%\hrule

>>>>

\begin{definition}{\emph{Matrices that define
      graphs.\cite[Def.~2.4]{d08phd}}} %
  \label{def:graphmatrices} %
  Let $G$ and $H$ be defined as follows. $G = (V,E_G)$ is a graph with
  vertex set $V = \{v_i \mid i \in [n]\}$ and edge set $E_G \subseteq
  \{(v_i,v_j) \mid i, j \in [n]\}$ such that $|E_G| = m$. $H = (A, B,
  E_H)$ is a bipartite graph with partitions $A = \{a_i \mid i \in
  [n_a]\}$ and $B = \{b_i \mid i \in [n_b]\}$.
  \begin{enumerate}[{\ref{def:graphmatrices}}--i.]
  \item \emph{Adjacency matrix} of $G$ is the symmetric $n \times n$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(v_i,v_j) \in E_G$
    for all $i,j \in [n]$.
  \item \emph{Augmented adjacency matrix} of $G$ is obtained from its
    adjacency matrix by setting all main diagonal elements to \un, \ie
    $m_{i,i} = \un$ for all $i \in [n]$.
  \item \emph{Maximal clique matrix} or \emph{vertex-clique incidence
      matrix} of $G$ is the $n \times k$ binary matrix $M$ with
    $m_{i,j} = \un$ \iff $v_i \in C_j$ for all $i \in [n], j \in [k]$
    where $\{C_j \mid j \in [k]\}$ is the set of maximal cliques of
    $G$.
  \item \emph{Half adjacency matrix} of $H$ is the $n_a \times n_b$
    binary matrix $M$ with $m_{i,j} = \un$ \iff $(a_i, b_j) \in E_H$
  \end{enumerate}
\end{definition}
\qed

\begin{figure}[t]
  \centering
  \begin{tabular}[h]{cccl}
    \figtabsize
    ${\bf G_1}$: 
    \includegraphics[scale=0.2]{../img/ex1_concaveroundgr.pdf} &
    ${\bf G_2}$: 
    \includegraphics[scale=0.2]{../img/ex2_intervalgr.pdf} &
    ${\bf H}$: 
    \includegraphics[scale=0.2]{../img/ex2_intervalgr.pdf} &
    \begin{tabular}[h]{l|llll}
      % ${\bf B}$:
      % &&&&\\
      ${\bf C}$ &$w_1$ &$w_2$ &$w_3$ &$w_4$\\
      \hline
      $u_1$ &\un   &\un   &0     &0   \\
      $u_2$ &\un   &\un   &\un   &\un \\
      $u_3$ &0     &0     &\un   &\un \\
      $u_4$ &0     &\un   &\un   &0   \\
      $u_5$ &\un   &\un   &\un   &0   
    \end{tabular}
  \end{tabular}\\

  \begin{tabular}{lll} 
    \begin{tabular}[h]{l|lll lll}
      % ${\bf A_1}$:  
      %&&&&&&\\
      ${\bf A_1}$ &$v_1$ &$v_2$ &$v_3$ &$v_4$ &$v_5$ &$v_6$\\
      \hline
      $v_1$     &0     &\un   &\un  &0     &\un   &\un \\
      $v_2$     &\un   &0     &\un  &\un   &0     &\un \\
      $v_3$     &\un   &\un   &0    &\un   &\un   &0   \\
      $v_4$     &0     &\un   &\un  &0     &0     &0   \\
      $v_5$     &\un   &0     &\un  &0     &0     &0   \\
      $v_6$     &\un   &\un   &0    &0     &0     &0   
    \end{tabular}
    & 
    \begin{tabular}[h]{l|llll}
      % ${\bf B}$:  
      %&&&&\\
      ${\bf B}$&$c_1$ &$c_2$ &$c_3$ &$c_4$\\
      \hline
      $v_1$ &\un   &\un   &\un   &0   \\
      $v_2$ &\un   &0     &0     &0   \\
      $v_3$ &0     &\un   &0     &0   \\
      $v_4$ &0     &0     &\un   &\un \\
      $v_5$ &0     &\un   &\un   &0   \\
      $v_6$ &0     &0     &0     &\un  
    \end{tabular}
    & 
    \\    
    && \\
    \begin{tabular}[h]{l|llllll}
      % ${\bf A_2}$:  
      %&&&&&&\\
      ${\bf A_2}$&$v_1$ &$v_2$ &$v_3$ &$v_4$ &$v_5$ &$v_6$\\
      \hline
      $v_1$ &\un   &\un   &\un  &0     &\un   &\un \\
      $v_2$ &\un   &\un   &\un  &\un   &0     &\un \\
      $v_3$ &\un   &\un   &\un  &\un   &\un   &0   \\
      $v_4$ &0     &\un   &\un  &\un   &0     &0   \\
      $v_5$ &\un   &0     &\un  &0     &\un   &0   \\
      $v_6$ &\un   &\un   &0    &0     &0     &\un 
    \end{tabular}    
    &
    \begin{tabular}[h]{l|llllll}
      % ${\bf A_3}$:  
      %&&&&&&\\
      ${\bf A_2'}$ &$v_1$ &$v_6$ &$v_2$ &$v_4$ &$v_3$ &$v_5$\\
      \hline
      $v_1$ &\un   &\un   &\un  &0     &\un   &\un \\
      $v_6$ &\un   &\un   &\un  &0     &0     &0   \\
      $v_2$ &\un   &\un   &\un  &\un   &\un   &0   \\
      $v_4$ &0     &0     &\un  &\un   &\un   &0   \\
      $v_3$ &\un   &0     &\un  &\un   &\un   &\un \\
      $v_5$ &\un   &0     &0    &0     &\un   &\un 
    \end{tabular}
   & \\

% ex3_convexbipartitegr.png  
  \end{tabular}

  \caption[\figtabsize Matrices defined in
  Def.~\ref{def:graphmatrices}]{\figtabsize $A_1$ is the
    {\em adjacency matrix} and $A_2$ is the {\em augmented adjacency matrix} of
    $G_1$. $A_2'$ is obtained from $A_2$ by permuting its rows
    and columns to achieve {\em \CROP order}, \ie $A_2$ has
    \CROP\,-- thus $G_1$
    is {\em a concave-round graph} (Def.~\ref{def:graphwithcop}~\ref{def::concave-round})
    and {\em a circular-arc graph} (Tab.~\ref{tab:graphmatrices})
    $B$ is the maximal clique matrix of $G_2$ and has \COP\,-- thus $G_2$ is an
    {\em interval graph}(Def.~\ref{def:graphwithcop}~\ref{def::concave-round}). $C$ is
    the half adjacency matrix of bipartite graph $H$ and has \COP on
    rows -- thus $H$ is {a convex bipartite graph}.} 
  \label{fig:graphmatrices}
\end{figure}

@@

{\tt tab~\ref{tab:graphmatrices} -}   \tnote{have an abridged version of table 2.1 in dom}

\begin{table}[htbp]
  \centering
 \caption{\figtabsize **** Graph matrices}
  \label{tab:graphmatrices}
\end{table}

@@

   \begin{enumerate}[\ref{def:graphwithcop}--i.]
   \item $G$ is \emph{convex-round} if its adjacency matrix has the
     \CROP.
   \item \label{def::concave-round} $G$ is \emph{concave-round} if its augmented adjacency matrix
     has \CROP. \tnote{cite BHY00} \tnote[minor]{add CROP to glossary}
   \item $G$ is an \emph{interval graph} if its vertices can be mapped
     to intervals on the real line \stt two vertices are adjacent \iff
     their corresponding intervals overlap \tnote{cite Ben59, Haj57}.
     $G$ is an interval graph \iff its maximal clique matrix has COP
     due to the result by \cite{gh64} which states that the maximal
     cliques of interval graph $G$ can be linearly ordered \stt for
     all $v \in V(G)$, cliques containing $v$ are consecutive in the
     ordering.
   \item $G$ is a \emph{unit interval graph} if it is an interval
     graph \stt all intervals have the same length.
   \item $G$ is a \emph{proper interval graph} if it is an interval
     graph \stt no interval properly contains another.
   \item $G$ is a \emph{circular-arc graph} if its vertices can be
     mapped to a set of arcs on a circle \stt two vertices are
     adjacent \iff their corresponding arcs overlap.
   \item $H$ is \emph{convex bipartite} if its half adjacency matrix
     has \COP on either rows or columns.
   \item $H$ is \emph{biconvex bipartite} or \emph{doubly
       convex}\cite{yc95} if its half adjacency matrix has \COP on
     both rows and columns.
   \item $H$ is \emph{circular convex} if its half adjacency matrix
     has \CROP.
   \end{enumerate}
\end{definition}
\qed
%\hrule
